Cloud Supercomputing

### 2019-04-11 writing/paper/paper.tex
Changed intro

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
\section{Introduction}
\subsection{The ExaHyPE-Engine}
The \exahype{} project (\url{www.exahype.eu}) develops an engine to solve arbitrary hyperbolic partial differential equations (\pde{}s) on upcoming exascale high performance computing architectures.
A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
The actual numerical scheme, domain decomposition and parallelisation techniques are left as a black box to the user.
Internally the \exahypeengine{} implements a high order \aderdg{} scheme on Legendre basis nodes.
The mesh is incorporated from the Peano framework~\cite{weinzierl2011}, which is based on spacetrees for Cartesian meshes.
The framework provides a distributed (\mpi{}) and shared memory (Intel \textsc{tbb}) parallelization tailored to dynamic adaptive mesh refinement (\amr{})~\todo{LR: ref}.
As the ADER-DG scheme is highly volatile as soon as shocks develop, we additionally provide \textit{a posteriori} finite volume limiting, recently\todo{Is 2016 recently? Originally developed in this paper, or just this special version?} developed by \citeauthor{dumbser2016simple} in~\cite{dumbser2016simple}.
We want to emphasize the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop}, which describes our communication-avoiding implementation of the whole numerical scheme.
\newcommand{\diffCoeff}{\varepsilon}%
\newcommand{\hyperFluxDef}{
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure)
  \end{pmatrix}
}%
\newcommand{\viscFluxDef}{
  \begin{pmatrix}
    0\\
     \stressT (\Q, \gradQ)  \\
     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}
   \end{pmatrix}
}%
We \todo{LR: General introduction is missing. Where do we see our paper, what has been done before? Here we should also introduce and describe the ExaHyPE-Engine as base of the paper} solve the compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
\begin{equation}
 \label{eq:equation-set} 
%  \begin{array}{l}
%  \text{mass cons.} \\
%  \text{momentum cons.} \\
%  \text{energy cons.} \\
%  \text{cont.\ gas} 
% \end{array}
% :
\quad
  \pdv{}{t}
  \underbrace{
  \begin{pmatrix}
    \Qrho\\
    \Qj\\
    \QE
    \end{pmatrix}}_{\Q}
  +
  \divergence{
  \underbrace{
  \left(
   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
+
\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
  \right)}_{\flux(\Q, \gradQ)}}
 =
  \underbrace{
  \begin{pmatrix}
    \source[\Qrho\phantom{\Qrho}]\\
    \source[\Qj]\\
    \source[\QE]
    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
\end{equation}
with vector of conserved quantitites $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
The conserved quantities
\begin{equation} 
  \label{eq:conserved-variables}
 \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
\end{equation}
are the density $\Qrho$, the two or three-dimensional momentum $\Qj$ and the energy density $\QE$.
The rows of \cref{eq:equation-set} are the conservation of mass, the conservation of momentum and the conservation of energy.

>>>>

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
\section{Introduction}
\subsection{The ExaHyPE-Engine}
The \exahype{} project (\url{www.exahype.eu}) develops an engine to solve arbitrary hyperbolic partial differential equations (\pde{}s).
A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
The underlying ADER-DG method, parallelisation techniques and dynamic adaptive mesh refinement are available for simulation while the implementations are left as a black box to the user.
An introduction to the communication-avoiding implementation of the whole numerical scheme can be found in the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop}.
In this paper we extended this generic approach for hyperbolic \pde{}s by parabolic terms.
We base this extension on the work of \citeauthor{gassner2008discontinuous} \cite{gassner2008discontinuous}, which has already been applied to the ADER-DG method in \cite{dumbser2010arbitrary}.
%Including these terms gives users the option to solve arbitrary parabolic \pde{}s \todo{LR: stimmt das ?}.
We want to emphasize that with this extension we add the option to limit the numerical scheme \todo{LR: ref Ja/Nein?} with viscosity terms. This will exploited in this paper in a series of scenarios for the compressible Navier-Stokes equations which implicitly include viscosity as part of the equation.

\newcommand{\diffCoeff}{\varepsilon}%
\newcommand{\hyperFluxDef}{
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure)
  \end{pmatrix}
}%
\newcommand{\viscFluxDef}{
  \begin{pmatrix}
    0\\
     \stressT (\Q, \gradQ)  \\
     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}
   \end{pmatrix}
}%
The compressible Navier-Stokes equations in the conservative form are defined as% \pcref{eq:conservation-law-gradient}
\begin{equation}
 \label{eq:equation-set} 
%  \begin{array}{l}
%  \text{mass cons.} \\
%  \text{momentum cons.} \\
%  \text{energy cons.} \\
%  \text{cont.\ gas} 
% \end{array}
% :
\quad
  \pdv{}{t}
  \underbrace{
  \begin{pmatrix}
    \Qrho\\
    \Qj\\
    \QE
    \end{pmatrix}}_{\Q}
  +
  \divergence{
  \underbrace{
  \left(
   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
+
\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
  \right)}_{\flux(\Q, \gradQ)}}
 =
  \underbrace{
  \begin{pmatrix}
    \source[\Qrho\phantom{\Qrho}]\\
    \source[\Qj]\\
    \source[\QE]
    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
\end{equation}
with vector of conserved quantitites $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
The conserved quantities
\begin{equation} 
  \label{eq:conserved-variables}
 \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
\end{equation}
are the density $\Qrho$, the two or three-dimensional momentum $\Qj$ and the energy density $\QE$.
The rows of \cref{eq:equation-set} are the conservation of mass, the conservation of momentum and the conservation of energy.
